\documentclass{article}

\usepackage{amsmath,amsfonts,amssymb}
\usepackage[landscape]{geometry}
\usepackage{graphicx}
\usepackage{ pstricks,pst-grad  }
\usepackage{wrapfig}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
 
\usepackage{color}
\usepackage{epstopdf}
\usepackage{framed}
 

 %  TikZ & PGF Libraries
\usepackage{tikz}
\usepackage{animate}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{decorations.pathmorphing,patterns}
\usepackage{calc}


 \input  {macros_1057.tex}

\renewcommand{\familydefault}{\sfdefault}

\textheight=6.5in
\textwidth=9.55in
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\topmargin = 0.0 in
\headheight = 0.0 in
\headsep = 0.0 in
\parskip = 0.2in
\parindent = 0.0in
\hfuzz=20pt
\overfullrule=0pt
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\pagestyle{empty}

 \sffamily
 
\bcenter
{\large \bf Homework 2 - Random Processes } \medskip
\ecenter

\vskip.25in
\hrule\smallskip\hrule
\medskip

\benum
\item Calculate the following probabilities.   {\red Justify your answers}
\benum
\item  Suppose you flip a fair coin 3 times.  What is the probability of heads coming up exactly two times?
\item Suppose you roll two fair 6-sided dice and sum the numbers that appear.  What is the probability of the sum being  9?
\item Suppose you roll two fair 6-sided dice and sum the numbers that appear.  What is the probability of the sum being less than 6?
\item  Suppose you roll two fair 8-sided dice and sum the numbers that appear.  What is the probability of the sum being exactly 2?
\item Suppose you roll two fair 6-sided dice and sum the numbers that appear.  What is the probability of the \textbf{complement} of the sum being greater than 10?
\eenum

\medskip \hrule \medskip


\item Calculate the expected value  for  the  following game and give the probability of each outcome occurring. Determine whether the house or the player has the advantage.  
{\red Justify your answers}
 \begin{quote}
In this game the player is asked to roll two 6-sided dice and sum the numbers appearing. It costs \$3 to play the game.  If the sum is a 6, 7 or 8 the player gets \$3 and the cost to play the game is returned (that is, the payoff is \$6).  If the sum is 12 the player gets \$10 and the cost to play is returned.  Otherwise the player loses the \$3 it cost to play.
\end{quote}
 

\medskip \hrule \medskip

\item  Calculate the following statistical measures for the exam scores given  below; the data   has a mean of 80.75.  You can check your answers using Python (or your scientific calculator) but the formulas  for each must be written down.  {\red Justify your answers}
$$ 84, 72, 98, 88, 76, 71, 81, 76$$
\benum 
\item Determine the median of the data. 
\item Determine the variance of the data.  Note:  use the formula for data variance, that is divide by the number of data points minus one. 
\item Determine the standard deviation for the data.

\eenum

\eenum
 \bigskip\hrule\smallskip\hrule
\bigskip

 

\end{document}

